%-------------------------
% Resume in Latex
% Author : Charles McCartney
% Based off of: https://github.com/sb2nov/resume, additional credit to Jake Gutierrez
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeExperienceHeading}[2]{
    \vspace{-2pt}
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}


\begin{center}
    \textbf{\Large \scshape Charles McCartney} \\ \vspace{1pt}
    \begin{tabular}{c}
    Roswell, GA 30076 $|$ +1-404-820-6505 $|$ \href{mailto:charleshmccartney@gmail.com}{charleshmccartney@gmail.com} \\ 
    \href{https://linkedin.com/in/charles-mccartney-hugh}{linkedin.com/in/charles-mccartney-hugh} 
    $|$
    \href{https://github.com/CHMcCartney}{github.com/CHMcCartney} $|$ U.S. and U.K. Citizen
    \end{tabular}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, GA}
      {Bachelor of Science in Computer Science; GPA: 3.76/4.00}{Aug. 2020 -- May 2024}
    \resumeItemListStart
        \resumeItem{Certification in Information Technology Management} 
        \resumeItem{Georgia Tech Oxford Study Abroad Program \hfill \emph{May 2022 -- Aug. 2022}}
    \resumeItemListEnd 
  \resumeSubHeadingListEnd
%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Georgia Tech Hacklytics} $|$ \emph{Data Science Hackathon}}{Feb. 2024}
          \resumeItemListStart
            \resumeItem{\textbf{Achievement: } Awarded Best Domain by Major League Hacking (NoLapse.tech)}
            \resumeItem{Aggregated SAMSHA data to evaluate the most significant correlative factors for relapse}
            \resumeItem{Implemented a random forest model to predict relapse probability using Sci-kit Learn, Pandas, and NumPy}
            \resumeItem{Created front-end dashboard to explore data insights using Gradio, HTML/CSS, and Python}
          \resumeItemListEnd 
      \resumeProjectHeading
          {\textbf{Epi Info Application Development} $|$ \emph{Centers for Disease Control and Prevention}}{Aug. 2023 -- Present}
          \resumeItemListStart
            \resumeItem{Updated and overhauled a mobile data collection app for epidemiological research, improving functionality}
            \resumeItem{Implemented data synchronization and sharing tools using Box cloud services and SQLite}
            \resumeItem{Translated outdated codebase to modern frameworks for compatibility, using Java and recent Android SDK/API }
            \resumeItem{Emphasized Agile methods, delivering well-documented artifacts, detailed demos, and continuous version updates}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Air Travel Relational Database Implementation} $|$ \emph{MySQL, RDBMS, Excel}}{Aug. 2023 -- Dec. 2023}
          \resumeItemListStart
            \resumeItem{Applied MySQL to initialize physical database schema and normalized input data for airport tracking system}
            \resumeItem{Provided supporting views and related procedures to enable a fully interactive and populated database}
          \resumeItemListEnd
      \resumeProjectHeading
        {\textbf{Taxi Fare Prediction Model Implementation} $|$ \emph{Python, NumPy, Pandas, Matplotlib, Git}}{Jan. 2023 -- May 2023}
        \resumeItemListStart
            \resumeItem{Configured large-scale datasets via Python using Pandas and NumPy for data cleaning and feature engineering}
            \resumeItem{Trained models via supervised learning algorithms such as Random Forest, Multiple Regression, Decision Tree, Lasso, Ridge, and Polynomial Regression for optimal performance on validation set and unseen data}
        \resumeItemListEnd
      \resumeProjectHeading
        {\textbf{Web-based Data Visualization} $|$ \emph{JavaScript, HTML/CSS, Python, D3.js}}{Jan. 2023 -- May 2023}
        \resumeItemListStart
            \resumeItem{Implemented a front-end interface for data exploration using HTML/CSS, JavaScript, and D3.js}
        \resumeItemListEnd
      \resumeProjectHeading
        {\textbf{Android Tower Defense Application} $|$ \emph{Agile, Java, Android Studio Code, Git}}{Jan. 2022 -- May 2022}
        \resumeItemListStart
            \resumeItem{Lead the creation of a a dynamic mobile application from scratch using Java and Android Studio Code}
            \resumeItem{Implemented Object-Oriented design principles to enhance code modularity and extensibility}
        \resumeItemListEnd
      \resumeProjectHeading
        {\textbf{Pong on GBA Emulator} $|$ \emph{Docker, C, Linux emulator}}{Sep. 2021 -- Nov. 2021}
        \resumeItemListStart
            \resumeItem{Manipulated video buffer and dynamic memory allocation using C within a Linux environment using Docker}
        \resumeItemListEnd
    \resumeSubHeadingListEnd
%-----------EXPERIENCE-----------
\section{Experience}
    \resumeSubHeadingListStart
        \resumeExperienceHeading
        {\textbf{Teaching Assistant} $|$ Design \& Analysis of Algorithms}{Aug. 2023 -- Dec. 2023}
        \resumeItemListStart
            \resumeItem{Contributed to creation of review materials and grading for a body of over 250 students}
            \resumeItem{Covered a wide range of topics including Divide \& Conquer, Graph Theory, and Dynamic Programming}
        \resumeItemListEnd
        \resumeExperienceHeading
        {\textbf{International Affairs Teacher} $|$ Model United Nations, Centennial HS}{Aug. 2019 -- May 2020}
        \resumeItemListStart
            \resumeItem{Formulated and delivered dynamic curriculum tailored for 9th to 12th grade students}
            \resumeItem{Assumed role as lead instructor for elective course, showcasing effective leadership and communication}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills / Interests}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: English -- native, French -- intermediate} \\
     \textbf{Programming}{: Java, Python, C, C\#, SQL, JavaScript, HTML/CSS, R, LaTeX} \\
     \textbf{Developer Tools}{: Git, Docker, Tableau, VS Code, IntelliJ, Android Studio, Google Colab, Jupyter Notebook} \\
     \textbf{Libraries}{: Pandas, NumPy, Matplotlib, Seaborn, Sci-kit Learn, PyTorch, Tensorflow, D3.js, Gradio} \\
     \textbf{Affiliations}{: GT Barbell Club, Alpha Tau Omega, Data Science @ GT} \\
     \textbf{Interests}{: Golf, Tennis, Piano, Chess, International History, Weight Training, Data Science \& ML Technology}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
